Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-28 paper/main_RA-L_v1_nadia.tex
Final changes of the day.. will continue tomorrow

\clearpage
\section{Experimental Validation} \label{Sec:Exp}
%\textcolor{red}{We should try to have page 5 start with this section, i.e. we must reduce 1 full column from the previous sections.}
\subsection{JT-DS Learning Performance  Evaluation}
To evaluate the proposed JT-DS learning algorithm we collected kinesthetic demonstrations on a 7-DOF KUKA LWR 4+ robot arm, for 6 different tasks (see Table \ref{tab:learning}) which require mimicking the demonstrated joint-space behavior while reaching for a single target in task space. These behaviors include (as shown in Fig. \ref{fig:behaviors} ):
\begin{itemize}[leftmargin=*]
\item \textit{(1-2) Tennis strokes:} For these particular behaviors, we guide the robot to perform a forehand and backhand stroke.  
\item \textit{(3-4) Pouring motions:} 
\item \textit{(5) Footstep-like motion:} This behavior begins with a straight leg, moving through a singularity, and finally bringing the knee up (Fig. \ref{fig:snapshot:c})
\item \textit{(6) Singularity motions:} 
\end{itemize}

For each behavior, we collected $M$ demonstrations consisting of ($14$-D) time-series $\boldsymbol{\xi}^{(i)} = \{\xi_1^{(i)},\dots,\xi_T^{(i)}\}$ for $i= \{1,\dots,M\}$. The $14$ dimensions in $\xi_t = [q_t,\dot{q_t}]^T$ correspond to joints angles and velocities. We also record the final task-space configurations ${x^*}^{(i)}$, which we assume is the attractor in task-space. The recordings are initially collected at a rate of 500 Hz. However, our learning approach does not require such a dense representation of the trajectories, hence we down-sample them to 25 Hz. The total number of demonstrations $M$ and samples per \textit{behavior dataset} $M^*T$ are provided in Table \ref{tab:learning}. Given these datasets, we seek to: 
\begin{enumerate}[leftmargin=*]
\item Verify that the learned \textit{behavior synergies} are capable of generating the desired joint-space behaviors.  
\item Find the dimensionality approach which yields the best trade-off between accuracy and model complexity; i.e. the least dimensions $\delta$ and synergies $K$.
\end{enumerate}
We thus evaluate three learning approaches with different dimensionality reduction algorithms: (1) None, (2) PCA and (3) K-PCA with RBF kernel.
We perform 10-fold cross-validation on all datasets, for each learning approach, with a training/testing ratio of $60 \%$. To evaluate the performance of each learning approach, we take the square root of the MSE defined in \eqref{eq:optim_error}, which we refer to as the joint-velocity RMSE. Performing such cross-validation in our case, is however not straight-forward, as our $\mathcal{A}(q)$ formulation has several hyper-parameters, namely the dimensionality $\delta$ of our lower-dimensional embedding $\phi(q)$ and the number of local behavior synergies $K$. Moreover, when using K-PCA (with RBF kernel $k(q,q') = \exp(-\frac{||q-q'||^2}{2\sigma^2})$) we must also find the optimal width $\sigma$ in the RBF kernel. Thus, for each fold and each learning approach we find the optimal hyper-parameters $\delta$, $K$ and $\sigma$ (when applicable), as follows:
\textcolor{red}{\begin{enumerate}[leftmargin=*]
\item Explain how optimal $\delta$ is computed for PCA. 
\item Explain how optimal $\delta$ and $\sigma$ are found for K-PCA.
\item Explain how optimal $K$ is computed for GMM.
\end{enumerate}}

@@

\begin{table*}[!t]
\scriptsize
\caption{Performance Comparison of Learning Approach with different Dimensionality Reduction Schemes. We present the \texttt{mean(std)} for the optimal lower-dimensional $d$ and behavior synergies $K$ and RMSE on training and testing set, found for every learning scheme over 10 runs.\label{tab:learning}}
\begin{center}
\begin{tabular}{cc|cc|cc}
    \hline
    \hline
    \multicolumn{1}{c}{\multirow{4}{*}{Behavior Dataset}} & \multicolumn{1}{c}{\multirow{4}{*}{Dim. Red. Approach}} & \multicolumn{4}{c}{\multirow{2}{*}{Optimal Parameters | Joint Velocity RMSE [$rad/s$]}}
	\\  
    & & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $\delta$}} & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $K$}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Train}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Test}}	\\ \\ \hline

@@

\subsection{Comparison with Cartesian DS + IK Solver}
We now evaluate the performance of the properties of JT-DS\footnote{With the optimal learning approach found in the previous section.} against a standard Cartesian motion generator + IK solver approach. In this evaluation we seek to compare the capabilities (or lack thereof) of both approaches to: 
\begin{enumerate}
\item Follow desired behaviors in both joint and task spaces.
\item Achieve fast computation/convergence time.
\item Transit through singular configurations. 
\end{enumerate}
We continue our evaluation on a 7-DOF robot arm, the KUKA LWR 4+. The robot is controlled on the joint position level (linearly interpolating from joint velocities) at a rate of $ 500 $ Hz. The resultant joint angles are filtered by a critically damped filter to avoid high torques.

>>>>

\clearpage
\section{Experimental Validation} \label{Sec:Exp}
%\textcolor{red}{We should try to have page 5 start with this section, i.e. we must reduce 1 full column from the previous sections.}
\subsection{JT-DS Learning Performance  Evaluation}
To evaluate the proposed JT-DS learning algorithm we collected kinesthetic demonstrations on a 7-DOF KUKA LWR 4+ robot arm, for 6 different tasks (see Table \ref{tab:learning}) which require mimicking the demonstrated joint-space behavior while reaching for a single target in task space. These behaviors include (as shown in Fig. \ref{fig:behaviors} ):
\begin{itemize}[leftmargin=*]
\item \textit{(1-2) Tennis strokes:} For these particular behaviors, we guide the robot to perform a forehand and backhand stroke.  
\item \textit{(3-4) Pouring motions:} We guide the robot to pour chips on a bowl. The first instance is without an obstacle in the workspace, which is demonstrated as a linear joint interpolation. The second instance is with an obstacle, where the human is seen folding the elbow and lowering the shoulder of the robot arm to avoid the obstacle. 
\item \textit{(5) Footstep-like motion:} We demonstrate a footstep motion which begins with a straight leg, moving through a singularity, and finally bringing the knee up.
\item \textit{(6) Singularity motions:} For this behavior we simulate joint trajectories in which the base rotates and all of the other joints are locked in a singular configuration.
\end{itemize}

For each behavior, we collected $M$ demonstrations consisting of ($14$-D) time-series $\boldsymbol{\xi}^{(i)} = \{\xi_1^{(i)},\dots,\xi_T^{(i)}\}$ for $i= \{1,\dots,M\}$. The $14$ dimensions in $\xi_t = [q_t,\dot{q_t}]^T$ correspond to joints angles and velocities. We also record the final task-space configurations ${x^*}^{(i)}$, which we assume is the attractor in task-space. The recordings are initially collected at a rate of 500 Hz. However, our learning approach does not require such a dense representation of the trajectories, hence we down-sample them to 25 Hz. The total number of demonstrations $M$ and samples per \textit{behavior dataset} $M^*T$ are provided in Table \ref{tab:learning}. Given these datasets, we seek to: 
\begin{enumerate}[leftmargin=*]
\item Verify that the learned \textit{behavior synergies} are capable of generating the desired joint-space behaviors.  
\item Find the dimensionality approach which yields the best trade-off between accuracy and model complexity; i.e. the least dimensions $\delta$ and synergies $K$.
\end{enumerate}
We thus evaluate three learning approaches with different dimensionality reduction algorithms: (1) None, (2) PCA and (3) K-PCA with RBF kernel.
We perform 10-fold cross-validation on all datasets, for each learning approach, with a training/testing ratio of $60 \%$. To evaluate performance, we take the square root of the MSE defined in \eqref{eq:optim_error}, which we refer to as the joint-velocity RMSE.

Performing such cross-validation in our case, is however not straight-forward, as our $\mathcal{A}(q)$ formulation has several hyper-parameters, namely the dimensionality $\delta$ of our lower-dimensional embedding $\phi(q)$ and the number of local behavior synergies $K$. Moreover, when using K-PCA (with RBF kernel $k(q,q') = \exp(-\frac{||q-q'||^2}{2\sigma^2})$) we must also find the optimal width $\sigma$ in the RBF kernel. Thus, for each fold and each learning approach we find the optimal hyper-parameters $\delta$, $K$ and $\sigma$ (when applicable), as follows:
\textcolor{red}{\begin{enumerate}[leftmargin=*]
\item Explain how optimal $\delta$ is computed for PCA. 
\item Explain how optimal $\delta$ and $\sigma$ are found for K-PCA.
\item Explain how optimal $K$ is computed for GMM.
\end{enumerate}}

@@

\begin{table*}[!t]
\scriptsize
\caption{\scriptsize Performance Comparison of Learning Approach with different Dimensionality Reduction Schemes. We present the \texttt{mean(std)} for the optimal lower-dimensional $d$ and behavior synergies $K$ and RMSE on training and testing set, found for every learning scheme over 10 runs.\label{tab:learning}}
\begin{center}
\begin{tabular}{cc|cc|cc}
    \hline
    \hline
    \multicolumn{1}{c}{\multirow{4}{*}{Behavior Dataset}} & \multicolumn{1}{c}{\multirow{4}{*}{Dim. Red. Approach}} & \multicolumn{4}{c}{\multirow{2}{*}{Optimal Parameters | Joint Velocity RMSE [$rad/s$]}}
	\\  
    & & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $\delta$}} & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $K$}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Train}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Test}}	\\ \\ \hline

@@

\subsection{Comparison with Cartesian DS + IK Solver}
We now evaluate the performance of JT-DS\footnote{With the optimal learning approach found in the previous section.} against a standard Cartesian motion generator + IK solver approach. In this evaluation we seek to compare the capabilities (or lack thereof) of both approaches to: 
\begin{enumerate}
\item Follow desired behaviors in both joint and task spaces.
\item Achieve fast computation/convergence time.
\item Transit through singular configurations. 
\end{enumerate}
We continue our evaluation on a 7-DOF robot arm, the KUKA LWR 4+. The robot is controlled on the joint position level (linearly interpolating from joint velocities) at a rate of $ 500 $ Hz. The resultant joint angles are filtered by a critically damped filter to avoid high torques.
